
    \begin{thebibliography}{}

    \bibitem[zh, 2019]{zh2019}{\fontsize{16pt}{\baselineskip}\selectfont{\it\bfseries 中文文獻}}

    \bibitem[方氏等人, 2011]{inbook3}
方氏、作者二與作者三（2011）。
\newblock  載於楊先生（主編），\textbf{一本書里的一部分內容}（頁 233-666）。楊先生: 中國社會科學出版社。

\bibitem[伍氏, 2011]{manual1}
伍氏（2011）。
\newblock 科技文檔題目。

\bibitem[李氏, 2012]{mastersthesis1}
李氏 (2012)。
\newblock \textbf{碩士畢業論文題目}。碩士論文，澳門科技大學。

\bibitem[online22, 无日期]{online22}
李氏(无日期)【GitHub】。澳門科技大學博士論文\LaTeX 模版,沒有日期信息。取自 https://github.com/iihciyekub/MUST-Thesis

\bibitem[online33, 2019年5月29日]{online33}
李氏(2019年5月29日)【GitHub】。澳門科技大學博士論文\LaTeX 模版,沒有作者與日期信息。取自 https://github.com/iihciyekub/MUST-Thesis

\bibitem[吳氏等人, 2011]{booklet34}
吳氏、作者二與作者三（2011）。
\newblock \textbf{ 沒有出版社的書籍書名}。澳門：中國社會科學出版社。

\bibitem[沈氏, 2012]{proceedings11}
沈氏 (2012)。
\newblock 會議論文集。

\bibitem[馬氏等人, 2011]{misc43}
馬氏、作者二、作者三、作者四、作者五、作者六、…與作者八（2011）。
\newblock MISC 類型題目。
\newblock \textbf{******學報}，\textbf{11}\textbf{(1)}，11-19。

\bibitem[陳氏, 2019]{phdthesis3}
陳氏 (2019)。
\newblock \textbf{博士畢業論文題目}。博士論文，澳門科技大學。

\bibitem[孫氏等人, 2011]{manualwew}
孫氏、作者二、作者三、作者四、作者五、作者六、…與作者八（2011）。
\newblock manual 技術手冊。
\newblock \textbf{******學報}，\textbf{11}\textbf{(1)}，11-19。

\bibitem[張者一等人, 2011]{book34}
張者一、作者二與作者三（2011）。
\newblock \textbf{ 有確定出版社的書籍書名}。澳門：iihciyekub出版社。

\bibitem[楊氏等人, 2012]{inproceedings22}
楊氏、作者二與作者三 (2012)。
\newblock 會議論文集中的一篇文章。

\bibitem[蔡氏等人, 2011]{article32}
蔡氏、作者二、作者三、作者四、作者五、作者六、…與作者八（2011）。
\newblock article 類型題目。
\newblock \textbf{******學報}，\textbf{11}\textbf{(1)}，11-19。

\bibitem[歐陽氏, 2012]{thesis2}
歐陽氏 (2012)。
\newblock \textbf{畢業論文題目}。論文，澳門科技大學。

\bibitem[online11, 2011年11月09日]{online11}
澳門科技大學博士論文\LaTeX 模版,沒有作者信息。(2011年11月09日)。取自 https://github.com/iihciyekub/MUST-Thesis

\bibitem[online33, 无日期]{online33}
澳門科技大學博士論文\LaTeX 模版,沒有作者與日期信息。(无日期)。取自 https://github.com/iihciyekub/MUST-Thesis

\bibitem[En, 2019]{en2019}{\fontsize{16pt}{\baselineskip}\selectfont{\it\bfseries 英文文獻}}

    \bibitem[online2e2, n.d.]{online2e2}
\iiname(n.d.)[GitHub].A \LaTeX Template For MUST Thesis without data info, Retrieved from https://github.com/iihciyekub/MUST-Thesis

\bibitem[online3e4, 2011,September 11]{online3e4}
\iiname(2011,September 11)[code resources].A \LaTeX Template For MUST Thesis without author \& data info, Retrieved from https://github.com/iihciyekub/MUST-Thesis

\bibitem[online3e3, n.d.]{online3e3}
A \LaTeX Template For MUST Thesis without author \& data info,(n.d.), Retrieved from https://github.com/iihciyekub/MUST-Thesis

\bibitem[online1e1, 2011,September 11]{online1e1}
A \LaTeX Template For MUST Thesis without author info,(2011,September 11), Retrieved from https://github.com/iihciyekub/MUST-Thesis

\bibitem[Alisa \& David, 2012]{mastersthesis}
Alisa, \& David (2012).
\newblock {\em Mastersthesistitle}. Master dissertation,  mac of Technology.

\bibitem[Delton, 2011]{inbook}
Delton, H. (2011).
\newblock  Semantic analysis. In Kongthon (Ed.), {\em Machine learning wtih something} (pp. 233-666). Kongthon: Acm Computing Surveys.

\bibitem[Fundel, 2007]{thesis}
Fundel, Katrin (2007).
\newblock {\em Text mining and gene expression analysis towards combined interpretation of high throughput data}. Dissertation, lmu.

\bibitem[Ignatow \& Mihalcea, 2016]{book1}
Ignatow, Gabe., \& Mihalcea, Rada. (2016).
\newblock {\em Text mining: a guidebook for the social sciences}. Sage Publications.

\bibitem[Kongthon, 2004]{phdthesis}
Kongthon, Alisa (2004).
\newblock {\em A text mining framework for discovering technological intelligence to support science and technology management}. Doctoral dissertation, Georgia Institute of Technology.

\bibitem[Macedo et al., 2009]{inproceedings}
Macedo, Alexandra Lorandi, Reategui, Eliseo, Lorenzatti, Alexandre, \& Behar, Patricia (2009).
\newblock Using text-mining to support the evaluation of texts produced collaboratively. Springer (pp. 368--377).

\bibitem[Sebastiani et al., 1988]{misc2}
Sebastiani, F. Salton, G1., Buckley, C2., Buckley, C3. Salton, G4., Buckley, C5., Buckley, C6.,..., \& Buckley, C32. (1988).
\newblock Term-weighting approaches in automatic text retrieval.
\newblock {\em Information Processing \& Management}, 513-523.

\bibitem[Talton et al., 2011]{booklet}
Talton, H., Buckley, W., \& Yue, R. (2011).
\newblock {\em Machine learning in automated text categorization}. Beijing:Acm Computing Surveys.

\bibitem[Teahan \& Harper, 2001]{proceedings}
Teahan, William J, \& Harper, David J (2001).
\newblock Combining ppm models using a text mining approach. IEEE (pp. 153--162).

\bibitem[Null, 2012]{manual}
Null (2012).
\newblock Technology manual.

\bibitem[Vickman, 2007]{article1}
Vickman, T. A. (2007).
\newblock The changing digital dynamics of multichannel marketing the feasibility of the weblog: text mining approach for fast fashion trending.
\newblock {\em Journal of Fashion Marketing and Management}, {\em 11}{\em (4)}, 604-+.

\end{thebibliography}
    